Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2012-04-26 paper/paper.tex
Resize figures
abstract

Large-scale computational applications represented as scientific workflows, are
often grouped into ensembles composed of several inter-related workflows. In
this paper, we address a new and important problem concerning the efficient 
management of such ensembles under both budget and deadline constraints on 
Infrastructure-as-a-Service (IaaS) clouds. IaaS clouds are characterized by
on-demand resource provisioning capabilities and a pay-per-use model.  We discuss,
develop, and assess algorithms based on static and dynamic strategies for both
task scheduling and resource provisioning. We assume that the workflows within
an ensemble are prioritized by the user. We evaluate the algorithms via
simulation using a set of scientific workflow ensembles with a broad range of
budget and deadline parameters, identify which algorithm performs best for 
different application scenarios and constraint ranges. We find that the key 
factor determining the performance of an algorithm is its ability to decide which
workflows in an ensemble to admit or reject for execution. The results
show that the admission procedure based on workflow structure and estimates of
task runtimes can significantly improve the quality of solutions.

>>>>

Large-scale computational applications represented as scientific workflows, are
often grouped into ensembles composed of several inter-related workflows. In
this paper, we address a new and important problem concerning the efficient 
management of such ensembles under both budget and deadline constraints on 
Infrastructure-as-a-Service (IaaS) clouds. IaaS clouds are characterized by
on-demand resource provisioning capabilities and a pay-per-use model.  We discuss,
develop, and assess algorithms based on static and dynamic strategies for both
task scheduling and resource provisioning. We assume that the workflows within
an ensemble are prioritized by the user. We evaluate the algorithms via
simulation using a set of scientific workflow ensembles with a broad range of
budget and deadline parameters, taking into account uncertainties in task runtime
estimations, provisioning delays and failures. We find that the key 
factor determining the performance of an algorithm is its ability to decide which
workflows in an ensemble to admit or reject for execution. The results
show that the admission procedure based on workflow structure and estimates of
task runtimes can significantly improve the quality of solutions.
